### 2025-03-30 base-rates.qmd
20250330 - update links

::: {#fig-probabilityNomogramLine}
![](images/probabilityNomogramLine.png){width=50% fig-alt="Probability Nomogram. (Figure retrieved from https://upload.wikimedia.org/wikipedia/commons/thumb/6/66/Fagan_nomogram.svg/945px-Fagan_nomogram.svg.png). Also provided in: @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Probability Nomogram Example. (Figure adapted from [https://upload.wikimedia.org/wikipedia/commons/thumb/6/66/Fagan_nomogram.svg/945px-Fagan_nomogram.svg.png](https://upload.wikimedia.org/wikipedia/commons/thumb/6/66/Fagan_nomogram.svg/945px-Fagan_nomogram.svg.png). Also provided in: @Petersen2024a and @PetersenPrinciplesPsychAssessment.)
:::

>>>>

::: {#fig-probabilityNomogramLine}
![](images/probabilityNomogramLine.png){width=50% fig-alt="Probability Nomogram. (Figure retrieved from https://commons.wikimedia.org/wiki/File:Fagan_nomogram.svg). Also provided in: @Petersen2024a and @PetersenPrinciplesPsychAssessment."}

Probability Nomogram Example. (Figure adapted from [https://commons.wikimedia.org/wiki/File:Fagan_nomogram.svg](https://commons.wikimedia.org/wiki/File:Fagan_nomogram.svg). Also provided in: @Petersen2024a and @PetersenPrinciplesPsychAssessment.)
:::
